\cvsection{Projects}

\begin{cventries}

	\cventry
		{University of Tennessee at Martin}
		{Peg Game: Software Engineering Term Project}
		{}
		{Spring 2023}
		{
		\begin{cvitems}
			\item A recreation of the classic Cracker Barrel peg game which features a move highlighting/checking algorithm and leaderboard.
			\item Designed to implement various design patterns to accomplish a goal (e.g., factory method, strategy pattern).
			\item \textbf{Technical Skills:} C\#, WPF framework, git, \LaTeX, Dia.
		\end{cvitems}
		}
		
	\cventry
		{}
		{UDPsend}
		{}
		{Feb 2022 - Nov 2022}
		{
		\vspace{-1.5em}
		\begin{cvitems}
			\item Tool to transmit UDP network packets to a specified address.
			\item Written as a personal assistance tool to help debug digital signage devices.
			\item \textbf{Technical Skills:} Python, Tkinter, \href{https://www.py2exe.org/}{py2exe}, git.
		\end{cvitems}
		}	
		
	\cventry
		{University of Tennessee at Martin}
		{Capstone Project: Tale of Adlez}
		{}
		{May 2023 - December 2023}
		{
%		\vspace{-1.5em}
		\begin{cvitems}
			\item Top-down, 2D, single-player action-adventure game designed using the Unity Engine. Heavily inspired by The Legend of Zelda series.
			\item Experienced developing in a git enviornment alongside other developers. Learned how to properly work in git, and how to manage branches, pull requests, and merges.
			\item \textbf{Technical Skills:} Unity, C\#, \LaTeX.
		\end{cvitems}
		}		

%	\cventry
%		{}
%		{}
%		{}
%		{Spring 2023}
%		{
%		\begin{cvitems}
%			\item 
%		\end{cvitems}
%		}
		



\end{cventries}
